\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Nripesh Niketan} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+447823766576}{+44 7823 766576}
    $|$
    \faAt \hspace{.5pt} \href{mailto:nripesh14@gmail.com}{nripesh14@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/nripeshn/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/NripeshN}{GitHub}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {University of Sheffield}{Sheffield, United Kingdom}
      {M.Sc. Cybersecurity and Artificial Intelligence}{Sep 2024 \textbf{--} Sep 2025}
      {}{}

    \resumeEducationHeading
      {Heriot-Watt University}{Dubai, UAE}
      {B.Sc. Computer Science}{Sep 2021 \textbf{--} Apr 2023}
      {Honors Degree in Artificial Intelligence}{Sep 2023 \textbf{--} Apr 2024}
    
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ Python ,C/C++, SQL } \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Docker, AWS, GCP, Azure, PyTorch, TensorFlow, Numpy, MySQL, MongoDB } \\ \vspace{3pt}
        
        \textbf{Methodologies:}{ Agile, Scrum, OOP, Functional Programming, DevOps, CI/CD} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
    {CrossGL}{Delaware, USA (Remote)}
    {CEO \& Founder}{May 2024 \textbf{--} Present}
      \resumeItemListStart
          \resumeItem{Founded \emph{\href{https://crossgl.net/}{\color{blue}{CrossGL}}}, a startup focused on creating cross-platform solutions for graphics rendering and hardware utilization.}
          \resumeItem{\textbf{Graphica Suite:} Led the development of a comprehensive suite of tools to unify shader languages, including:
            \begin{itemize}
              \item \emph{\href{https://github.com/CrossGL/crosstl}{\color{blue}\textbf{CrossTL:}}} Developed a Python AST-based translator capable of converting shader code into multiple target languages (HLSL, GLSL, Metal, SPIR-V, etc.), achieving over 2,500 monthly downloads on PyPI.
              \item \textbf{CrossGL Compiler:} Built a custom shader language, leveraging MLIR and LLVM, that compiles directly to binaries for backends like DirectX, OpenGL, Vulkan, and Metal, eliminating the need for manual shader porting.
            \end{itemize}}
          \resumeItem{\textbf{Dyson Platform:} Engineered a unified hardware abstraction layer addressing hardware fragmentation across CPUs, GPUs, TPUs, and FPGAs:
            \begin{itemize}
              \item Created an API platform enabling users to access and utilize hardware across major cloud providers (AWS, GCP, Azure, Intel, NVIDIA).
              \item Designed an AI agent to intelligently route tasks to the most suitable hardware based on user requirements, optimized for High-Performance Computing (HPC) scenarios like physics simulations.
            \end{itemize}}
          \resumeItem{Led a team of 20 engineers, driving the design, development, and deployment of innovative solutions.}
          \resumeItem{Actively raising pre-seed funding, securing partnerships with cloud providers, and negotiating credits worth \$500K across AWS, GCP, and Azure.}
          \resumeItem{Collaborated with industry stakeholders, cloud service providers, and key clients to define project roadmaps and ensure alignment with market needs.}
      \resumeItemListEnd

        \vspace{20pt}

    \resumeSubheading
      {The Applied AI Company (AppliedAI)}{Abu Dhabi, UAE}
      {AI/ML Engineer}{Mar 2024 \textbf{--} Apr 2024, Internship}
        \resumeItemListStart
            \resumeItem{Spearheaded the development of an innovative AI application designed to streamline medical coding processes, enhancing efficiency for medical clients.}
            \resumeItem{Engineered and deployed robust Python scripts using AWS Lambda and SQS workflows, ensuring scalable and reliable application performance.}
            \resumeItem{Leveraged OpenAI API to automate the extraction and processing of data from medical reports, significantly reducing manual coding errors and workload.}
            \resumeItem{Integrated Retrieval-Augmented Generation (RAG) and vision technologies to accurately interpret and categorize complex medical information, improving the accuracy of medical billing and coding.}
        \resumeItemListEnd

        \vspace{20pt}
        \resumeSubheading
        {Unify}{London, United Kingdom (Remote)}
        {DevRel Lead}{Nov 2023 \textbf{--} Apr 2024, Full-time}
          \resumeItemListStart
              \resumeItem{Initiated and maintained a collaboration with Vaunt to establish a recognition and award system for community contributors.}
              \resumeItem{Spearheaded community outreach initiatives to strengthen developer engagement and promote active participation in open-source projects.}
              \resumeItem{Managed the entire volunteer pipeline, including recruitment, hiring, onboarding, and promotion.}
              \resumeItem{Implemented structured processes for volunteer engagement, enhancing their experience and fostering growth.}
              \resumeItem{Actively contributed to projects, leveraging technical expertise to ensure the delivery of high-quality solutions.}
              \resumeItem{Served as the primary communication bridge between the development team and external contributors, facilitating effective idea exchange and feedback.}
              \resumeItem{Streamlined collaboration and problem-solving efforts, improving the efficiency and productivity of development endeavors.}
              \resumeItem{Represented Unify at various forums and events, advocating for our technologies and enhancing the company's reputation.}
              \resumeItem{Created tasks and ideas for projects and hackathons, fostering innovation and practical application of technologies.}
              \resumeItem{Developed automation for the contributor program using Google App Script, GCP functions, and GitHub CI/CD, optimizing operational processes.}
          \resumeItemListEnd      

          \resumeSubheading
          {Unify}{London, United Kingdom (Remote)}
          {Machine Learning Engineer}{Jun 2023 \textbf{--} Dec 2023, Internship}
            \resumeItemListStart
                \resumeItem{Engineered a custom Python code reformatter specifically for Ivy's backend, enhancing code organization and logical flow.}
                \resumeItem{Implemented intelligent sorting of code components such as imports, classes, functions, and variable assignments for improved consistency.}
                \resumeItem{Advanced code readability by intelligently clustering related functions and automating the insertion of explanatory headers.}
                \resumeItem{Devised a sophisticated file pattern recognition algorithm to enforce uniform formatting across specific file types.}
                \resumeItem{Pioneered the integration of Apple Silicon GPU acceleration into Ivy, significantly boosting performance on next-generation devices.}
                \resumeItem{Acted as the main liaison for a key Ivy contributor, streamlining communication, feedback assimilation, and joint problem-solving efforts.}
                \resumeItem{Continuously involved in the evolution and refinement of the code formatter, keeping it abreast of the latest industry advancements.}
                \resumeItem{Integral in the design and creation of machine learning algorithms and systems within Ivy's core development team.}
                \resumeItem{Contributed extensively to Ivy's open-source GitHub repository, focusing on Jax, PaddlePaddle, Tensorflow, and PyTorch frontends.}
                \resumeItem{Coordinated and oversaw the approval of Pull Requests, ensuring their quality aligns with Ivy's standards before integration.}
                \resumeItem{Collaborated with a diverse team of developers and data scientists to elevate software efficiency and reliability.}
                \resumeItem{Persistently explored and adopted cutting-edge technologies and frameworks to remain at the forefront of machine learning innovation.}
                \resumeItem{Rose to the position of Lead Volunteer, orchestrating the efforts of over 85 volunteers in various initiatives and projects.}
            \resumeItemListEnd

            \vspace{20pt}
            \resumeSubheading
            {Copeland}{Dubai, UAE}
            {Information Technology Business Analyst}{Jun 2023 \textbf{--} Jul 2023, Internship}
              \resumeItemListStart
                  \resumeItem{Designed and implemented a multi-threaded web scraper using Python's Selenium WebDriver to automate data extraction from a secure online portal, handling login authentication and dynamic page navigation.}
                  \resumeItem{Optimized performance with multi-threading by utilizing Python's threading module to parallelize the web scraping process, significantly reducing overall execution time.}
                  \resumeItem{Implemented a semaphore to regulate the number of concurrent threads, effectively controlling system resource usage and ensuring scalability without overloading system capabilities or breaching website's request limits.}
                  \resumeItem{Improved code modularity and reusability by creating reusable functions for tasks such as logging in and navigating website pages, enhancing code readability, maintainability, and reusability.}
                  \resumeItem{Managed error handling and exceptions robustly, ensuring consistent performance and data integrity of the scraper.}
              \resumeItemListEnd
          

            \vspace{20pt}
            \resumeSubheading
            {Emerson}{Dubai, UAE}
            {Information Technology Business Analyst}{Jun 2022 \textbf{--} Jun 2023, Internship}
              \resumeItemListStart
                  \resumeItem{Automated ASN upload process on Oracle using Python and Power Automate, reducing operational time by two days per week.}
                  \resumeItem{Developed multiple ETLs in Domo to streamline data transformations and analytics, enhancing data processing capabilities.}
                  \resumeItem{Implemented advanced data transformations for data science applications using Python, Pandas, Numpy, and Domo's API, improving data utilization and insights.}
                  \resumeItem{Created Python programs utilizing the Oracle\_cx module for efficient data extraction, transformation, and mass data uploads, optimizing data management processes.}
                  \resumeItem{Developed a web scraper in Python to automate data extraction from Teamcenter, enabling automatic downloads of specified files and saving 2 hours of work per day.}
                  \resumeItem{Assisted users in creating sophisticated Excel sheets with advanced formulas and functions, enhancing data organization and analysis efficiency.}
                  \resumeItem{Employed Python and Tesseract OCR to develop a machine learning model that converts images of data into Excel spreadsheets, substantially streamlining the data entry process.}
              \resumeItemListEnd

            \vspace{20pt}
            \resumeSubheading
            {Heriot-Watt University}{Dubai, UAE}
            {Football Club President}{Sep 2022 \textbf{--} Jun 2023, Part-time}
              \resumeItemListStart
                  \resumeItem{Oversaw all club operations, demonstrating strong leadership and management skills, ensuring effective club management and member satisfaction.}
                  \resumeItem{Organized events and managed budgets, fostering club success and growth through strategic financial planning and event management.}
                  \resumeItem{Hired and coordinated coaching staff to enhance team performance, improving player skills and team dynamics.}
                  \resumeItem{Utilized advanced Excel techniques to develop sophisticated scoring and point table systems for tournaments, increasing the accuracy and professionalism of club competitions.}
                  \resumeItem{Maintained accurate inventory records using well-organized Excel sheets, ensuring efficient management of club resources.}
                  \resumeItem{Collaborated effectively with team members and university officials to promote the club and secure necessary support and resources.}
              \resumeItemListEnd

    
  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Advanced Standing and Scholarship:}{ Awarded for scoring above 85\% in CBSE 12th finals, resulting in the skipping of the first year and receiving a 50\% scholarship at Heriot-Watt University. (2021)} \\ \vspace{3pt}

        \textbf{Dr. APJ Abdul Kalam Award for Outstanding Student:}{ Awarded to the top-performing students annually throughout India, recognizing exceptional academic and extracurricular achievements. (2019)}
    }}
  \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Panthon} $|$ \emph{\href{https://github.com/NripeshN/panthon}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Developed Panthon, a Python pip package, alongside \href{https://www.linkedin.com/in/arunimask/}{\color{blue}Arunima santhosh Kumar}. It serves as a comprehensive cybersecurity attack simulation library, encompassing a wide array of attacks including DoS, SQL injection, DNS spoofing, and MITM, aiming to enhance security testing capabilities.}
          \resumeItemListEnd
      
      \resumeProjectHeading
        {\textbf{Athena} $|$ \emph{\href{https://github.com/NripeshN/Athena}{\color{blue}GitHub}}}{}
          \resumeItemListStart
          \resumeItem{Developed Athena, a framework for enhancing the accuracy of Large Language Models (LLM) by integrating external tools such as Google Calendar, Wolfram Alpha, a code interpreter, and OpenWeather. Aimed to extend the functionality and applicability of LLMs across various real-world tasks.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd


%----------- CERTIFICATES -----------

\section{Certificates}
  \resumeSubHeadingListStart
    
    \resumeOrganizationHeading
      {Google}{May 2022}{IT Automation with Python Specialization}
    
    \resumeOrganizationHeading
      {Google}{May 2022}{Data Analytics Specialization}

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
